Deciding to Disclose

### 2015-09-15 Conclusion.tex
Explain the homophily situation better

From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant. The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable. By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.  Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

>>>>

From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant. There is a high level of uncertainty in the overall dynamics with the model free rules. This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation. By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.
